### 2022-08-04 main/chapter_2ljets.tex
flesh out summary cov and parameters

\section{Results}
\label{sec:2ljets_results}

Main results from the $\twoljets$-electroweak search have already been
presented in Section~\ref{sec:2ljets_splash} and sprinkled throughout this
chapter.
This section reports some ancillary results.

\TODO{Discuss and tie these together.}

A pre-fit (fitted to control regions but not signal regions) summary plot
is displayed in Figure~\ref{fig:2ljets_summary_no_sr}.

The correlation matrix of parameters, estimated from the inverse Hessian at
the best fit point and reduced to its most correlated parameters, is displayed
in Figure~\ref{fig:2ljets_fit_corrmatrix}.

All fitted parameters and their marginal error bars are displayed in
Figure~\ref{fig:2ljets_fit_parameters}.

Preliminary projected exclusion contours that separate the use only subsets
of our signal regions to assess their effects are displayed in
Figure~\ref{fig:2ljets_fit_muti_contourss}.

>>>>

\section{Results}
\label{sec:2ljets_results}
Main results from the $\twoljets$-electroweak search have already been
presented in Section~\ref{sec:2ljets_splash} and sprinkled throughout this
chapter.
This section reports some ancillary results.

\paragraph{Summary}
As I have argued incessantly, pre-fit predictions are useful because they can
actually be predictions to be tested by the data.
Our post-fit summary plot has previously been displayed in
Figure~\ref{fig:2ljets_summary}.
Its alternative version that does not fit to signal region data is shown here
in Figure~\ref{fig:2ljets_summary_no_sr}.
Since the significance measure is meaningful for this pre-signal-region plot,
we see that despite the inflated uncertainties in SR-Low, its bins still have
substantial deficits.
Validation region data are notably better predicted by this prediction;
as the post-fit result tunes itself to signal region data, coupled variations
lead to worse predictions in the validation regions (that are not included
directly in either fit).

\paragraph{Correlations}
All parameters are initially independent.
If the \heplikelihood\ is related to a probability distribution of parameters,
however, then they gain interdependencies when coupled through the likelihoods
of control and signal region data.
The the correlation matrix of parameters, estimated from an approximate Hessian
matrix at the best fit \heplikelihood, is displayed in
Figure~\ref{fig:2ljets_fit_corrmatrix}.
To reduce this matrix to a more readable size, only the most correlated
parameters are shown.

Mixed contributions of $\ttbar$, $\zjets$ and \diboson\ in the control regions
leads to anticorrelations between their normalization factors
``\texttt{mu\_*}'' that are seen in the bottom right corner of this correlation
plot.
Since statistical errors ``\texttt{gamma\_stat\_*}'' in control regions are not
absorbed into the sample-specific normalization factors, they are also
anticorrelated with normalization factors.
Similarly, the extra uncertainty for $\zjets$ in CR-tt causes an
anticorrelation between its parameter ``\texttt{alpha\_Zjets\_bextrap}''
and the $\ttbar$ normalization.
The failure of statistical precision in SR-Low-2 causes large systematic
variations that appear as the anticorrelations between
\texttt{gamma\_stat\_SRLow2\_cuts\_bin\_0} and numerous experimental
uncertainties.
Correlations between the $\zyjets$ normalization and $\ttbar$ uncertainties
are due to large variations in the alternative $\ttbar$ samples in \crdy.
Electron identification variations ``\texttt{alpha\_el\_chargeid\_*}'' have
some impact in SR-Low,  so are correlated with the $\zjets$ alternative sample
comparison ``\texttt{alpha\_Zjets\_alt}''.
Note that the up and down variations of parameters need not correspond to up
and down variations of yields in any region, so the signs of these correlations
are no necessarily meaningful.

\paragraph{Parameters}
Correlations between parameters do not indicate their central values.
To inspect individual parameters in the same fit to control and signal regions,
Figure~\ref{fig:2ljets_fit_parameters} displays all fitted parameters and their
marginal error bars.

Parameters named ``\texttt{$\alpha$\_*}'' are centred on zero with unit initial width,
and others are initially relative to $1$ with variable error bars.
Internally, plots like this are considered good if all parameters sit on
the central vertical line, with the motivations that normalization factors
should be close to $1$ (the predicted cross-sections are accurate) and that
our data should not compete with the precision of the studies that defined
our systematic variations.
That is, if we constrain a parameter by squeezing its error bar, then our data
could be better used to calibrate that parameter throughout the Collaboration.

I added the red arrow to indicate the $\zjets$ alternative sample comparison,
named ``\texttt{$\alpha$\_Zjets\_alt}'' here, that has disappeared off the
right-hand edge due to its best-fit value of $1.86 \pm 0.69$.
(see Section~\ref{sec:2ljets_zjets_alt}).
Its anticorrelation with the electron charge identification variations is
explained by their movement to negative values;
positive \texttt{$\alpha$\_Zjets\_alt} and negative
\texttt{$\alpha$\_el\_chargeid\_*} both reduce yields in SR-Low.

Several of the $\ttbar$ alternative-sample comparisons are also pulled away
from zero.
Some of this effect is explained by the drastic variation of
\texttt{$\alpha$\_Zjets\_alt}, that nearly doubles $\zjets$ yields in CR-tt
(see Table~\ref{tab:2ljets_zjets_alt}).
Much of the remainder is due to the alternating deficit and excess in
SR-OffShell-a and SR-OffShell-b respectively;
in particular, the
final state radiation (\texttt{$\alpha$\_ttbar\_fsr}) and
hard scatter (\texttt{$\alpha$\_ttbar\_hs}) variations both move $\ttbar$
yields in opposite directions in SR-OffShell-a and SR-OffShell-b, so the
movements of these parameters help to fit both deviations simultaneously.

\paragraph{Contours}
Preliminary projected exclusion contours that separate the use only subsets
of our signal regions to assess their effects are displayed in
Figure~\ref{fig:2ljets_fit_muti_contourss}.
